Best Practices for Alchemical Free Energy Calculations : v\versionnumber

### 2020-11-03 review_response/Responses.tex
last bibliography update

\documentclass[10pt,stdletter]{newlfm}
\usepackage{charter}
\usepackage{xcolor}

\widowpenalty=1000
\clubpenalty=1000

\newsavebox{\Luiuc}
\sbox{\Luiuc}{%
    \parbox[b]{1.75in}{%
        \vspace{0.5in}%
        \includegraphics[scale=0.2,ext=.pdf]
        {logo.pdf}%
    }%
}%

\makeletterhead{Uiuc}{\Lheader{\usebox{\Luiuc}}}

\newlfmP{headermarginskip=5pt}
\newlfmP{sigsize=5pt}
\newlfmP{dateskipafter=20pt}
\newlfmP{addrfromphone}
\newlfmP{addrfromemail}
\PhrPhone{Phone}
\PhrEmail{Email}

\lthUiuc

\namefrom{Antonia Mey}
\addrfrom{%
    University of Edinburgh\\
    David Brewster Road\\
    Edinburgh\\
    EH9 3FJ, UK\\ 
}

\phonefrom{ +44 131 651 3309}
\emailfrom{antonia.mey@ed.ac.uk}

\addrto{%
Living Journal of Computational Molecular Science}

\greetto{Dear Prof Oostenbrink,}
\closeline{Sincerely,}
\begin{document}
\begin{newlfm}

[fix me]

\textbf{Reviewer 1 comments:}
The best practices guide “Best Practices for Alchemical Free Energy Calculations” by Mey et al. gives an extensive introduction to the field of alchemical free energy calculations. After a general introduction, the reader is introduced to the statistical mechanics foundations needed to understand the concepts introduced later, followed by general discussions on applicability and prerequisites of free energy calculations. The authors then continue to discuss practical methodologies and issues and guide the reader towards a general understanding on how such calculations can be performed, including proper data analysis. It is then concluded that it is important to understand the functionalities and limitations of today’s often highly automated free energy workflows and that blind prediction challenges help to understand the used algorithms and issues related to reproducibility better.

The manuscript is very well-written and concepts of alchemical free energy calculations are clearly presented. The provided checklist can be a useful tool and can serve as initial orientation, especially for scientists who are new to the field.

@@

Figure 1: For me there is no intrinsic difference between the free energy calculations shown in panel D and F, both transformations should be performed in the bound and unbound states to obtain meaningful results, and both should be termed relative calculations (ΔΔG). Maybe it could be more clearly indicated in general if a whole molecule is decoupled and if only a part of a molecule is transformed?
\textcolor{red}{JS: swapped dG to ddG; swapped E and F, made 'Host' and 'membrane' text larger, added interaction schematic (green) in D}

@@

Section 4.1, line 30: it is not entirely clear to me what the authors mean by “edges”. This should be better explained in the text.

@@

@@

Section 5.4, last paragraph: I would call it “binding free energy prediction”, not “binding energy prediction”

Constraints and relative free energy calculations: for me, a timestep of 1 fs is more an upper limit for MD simulations involving non-constrained bonds, I would rather suggest a value of 0.5 fs.
\textcolor{MRS: This is a valuable point to raise. Certainly 1.0 fs is near the limit of stability without any constraints with standard fields, and there are studies showing there are nonnegligible statistical mechanical errors with timesteps of 1.0 fs. However, many studies with free energy calculations have been done with these parameters and it's not clear they have statistically significant deviation from simulations without simulations. We have added a discussion of timestep to section XXXX with a tentative recommendation that 1.0 fs may be sufficient, but some warnings there may be potentially be issues}

@@

\textcolor{red}{AR: We changed the wording to clarify this point. The reweighting can be skipped if the ligand is never \textit{sampled} while hitting the wall because, in this case, the numerical correction is exactly zero. Using the restraint is different from using no restraining potential at all because during the MD simulation the ligand might still very occasionally hit the wall (thus limiting its volume to the binding site) even if we these events are not observed after subsampling the trajectory.}

@@

\textcolor{red}{AR: We added the reference to the text.}

@@

\textcolor{red}{AR: Both the text in the section and the figure were updated to include the forward/reverse convergence test.}

@@

\textbf{Reviewer 2 Comments}
-Much of the discussion is related to alchemical free-energy calculations in drug design. I think that the success of such calculations is also very dependent on the force field. Although not a topic of the present manuscript, the authors may want to issue a recommendation/warning regarding the validation of automatically generated ligand topologies. I guess, many practitioners just take such topologies for granted.

\color[red]{We have added explicit comments in section 4.1 with respect to the need for using reasonable parameter/topology input files that have been inspected to make sure the molecular description has no obvious errors, or lack of chemical coverage in the method used to generate them}

-In the list of more advanced topics on page 3 the application to QM/MM simulations may be mentioned as well, since this seems to be an area of growing importance

\color[red]{MRS: we have added QM/MM explicitly in that list as an advanced topic beyond the scope of this document.}

-At the end of section 7.1.1 on pages 15/16 the following statement appears: “Typical molecular dynamics engines are not set up to recognize this change, or at least not to correctly include contributions to the free energy from changing constraints/constraint length, so results for a transformation would usually be erroneous.” This statement is a bit surprising since methods to calculate the contribution of the work done by constraint forces have been described a few times, e.g.: 
-Van Gunsteren, W.F., In van Gunsteren W.F. and Weiner, P.K. (Eds.) Computer Simulation of Biomolecular Systems: Theoretical and Experimental Applications, ESCOM, Leiden, 1989, pp. 1-26.

-Pearlman, D.A., Kollman, P.A., The overlooked bond-stretching contribution in free energy perturbation calculations, J. Chem. Phys. 1991, 94(6), 4532-4545.

-Straatsma, T.P., Zacharias, M., McCammon, J.A., Holonomic constraint contribution to free energy differences from thermodynamic integration molecular dynamics simulations, Chem. Phys. Lett., 1992, 196(3-4), 297-302.

-Pearlman, D.A., Determining the contributions of constraints in free energy calculations: Development, characterization, and recommendations, J. Chem. Phys. 1993, 98(11), 8964-8957.

One implementation, based on integrating over the constraint forces, can for example be found in the MD code GROMOS. I suggest to mention the availability of both the theory and also practical implementations in the manuscript.

\color[red]{We have revised this text in 7.1, making it clear that the corrections are known, that different programs vary in their implementation of the corrections, and that users should check the user manuals if they have bond lengths that both change and are constrainted}

-In section 7.2.2, when discussing changes in net charge the “Double-system/single-box” setup described by Gapsys et al. may be mentioned. It is related to the alchemical ion approach but can be mentioned here for completeness and to help newcomers to the field in sorting the various approaches. Gapsys, V., Michielssens, S., Peters, J. H., DeGroot, B. L., Leonov, H. Calculation of Binding Free Energies, In Andreas Kukol (ed.), Molecular Modeling of Proteins, Methods in Molecular Biology, vol. 1215, doi: 10.1007/978-1-4939-1465-4\_9, Springer Science+Business Media New York 2015.

@@

-In the list of symbols on page 4, the quantity $\Delta G$ is denoted as Gibbs free energy while $\Delta A$ is denoted as Helmholtz free energy. However, according to IUPAC or IUPAP these quantities are referred to as Gibbs energy or Helmholtz energy (see \url{https://doi.org/10.1039/9781847557889} or \url{https://doi.org/10.1016/0378-4371(78)90209-1}) or sometimes also as “Gibbs function” or “Helmholtz function” or as “free enthalpy” or “free energy” respectively. Of course, the nomenclature used by authors is very common in the field. Therefore, one solution would be to use the IUPAC nomenclature in the List of Symbols along with a footnote explaining that here a different nomenclature is used (or the other way round).

\color[red]{MRS: we have added the less-commonly used but also correct terms as alternate names for these quantities in the list of symbols.}

-Eq. (2) holds for dilute solutions if thermodynamic activities can be approximated by concentrations. This is also stated in the classical Gilson paper but I guess repeating it here, could be useful.

-Page 5: In statistical mechanics nomenclature the term “configuration” is usually used for q ⃑. In chemistry and biology, the term “conformation” is probably more common. In the context of the present manuscript “configuration” fits better in my opinion.

-The quantity $\Delta G_{solvated}$ in Figure 2 is called $\Delta G_{unbound}$ in Eq. (9).

-In the first paragraph of section 4.2 it is mentioned that a good practice is to perform two or three runs of the same perturbation. Here one might add that the initial conditions (i.e. velocities) should be different.

-Page 17, line 9 under Eq. (17): A, B, and AB may be replaced by R, L, and RL.

-In the paragraph of author contributions, the description of the contribution of Samarjeet Prasad seems to be missing.

TYPOS OR OTHER EDITORIAL ISSUES

-Page 3, right column, line 5 in third paragraph: preparation( Sec. 6) -> preparation (Sec. 6)

\textcolor{red}{JS: Fixed.}

-Page 4, left column, list of acronyms: “unsigned error” should be written in upper case to be consistent with the other entries.

\textcolor{red}{JS: Fixed.}

-Page 5, left column: In the nominator and denominator of Eqs (5) and (6) the minus sign is missing in the exponentials.

\textcolor{red}{JS: Fixed.}

-Page 5, right column, first line: “one of the …”

\textcolor{red}{JS: Fixed.}

-Page 6, right column, two lines above Eq. 12: Bennet’s -> Bennett’s

\textcolor{red}{JS: Fixed.}

-Page 8, right column, fifth line below Eq. 16: enrgies -> energies

\textcolor{red}{JS: Fixed.}

-Page 8, right column, 10th line below Eq 16: Perhaps the line break in the unit can be avoided.

\textcolor{red}{JS: Fixed by changing line to ..If the accuracy of \textit{a collection of} free energy calculations is..}

-Page 11, left column, paragraph 5.4: there are two occurrences of the term “binding energy prediction”. Is “binding free energy prediction” meant?

\textcolor{red}{JS: Fixed.}

-Page 12, left column: “stereoisomers” is misspelled.

\textcolor{red}{JS: Fixed.}

-Page 15, Figure 4: the right structure in the lower part has no green area. Is that intended?

\textcolor{green}{JS: Yes, as this structure does not match the MCS. Could perhaps be explained more clearly in the text?(subsection "ring breaking and forming"}

-Page 17, Eq. 18: the ratio of $c^o/V_L$ seems not correct. It should be either $V^o/V_L$ where $V^o$ is the volume corresponding to $c^o$, or, when sticking to $c^o$: $c^o * V_L$

\textcolor{green}{JS: leaving this up to Toni"}

-Page 17, line 14: “restraints” (s was missing)

\textcolor{red}{JS: Fixed.}

-Page 19, Figure 7: The axis labels are hard to read.

\textcolor{red}{JS: Fixed in PR.}

-Page 19, Eq. 19: I think it should be $(1-\lambda)U_0 + \lambda U_1$ to fit to the text below the equation

\textcolor{green}{JS: leaving this up to Toni"}

-Page 20, left column, line 14: σ/r should be written in parenthesis.

\textcolor{red}{JS: Fixed.}

-Page 20, left column, line 16: B in $k_BT$ should be in subscript and T not.

\textcolor{red}{JS: Fixed.}

-Page 20, left column, line 10 from the bottom: is there an “at” missing in “and at the other endpoint …”?

\textcolor{red}{JS: Yes, fixed.}

-Page 22, left column, caption of Figure 8 (line 6): should there be a comma after “exchange”?

\textcolor{green}{JS: I don't see it?}

-Page 22, right column, line 2: though -> through

\textcolor{red}{JS: Fixed.}

-Page 22, right column, lines 8 and 9: Please add a blank between value and unit.

\textcolor{red}{JS: Seems to have been fixed by DM.}

-Page 22, right column, last line of second paragraph: Please remove blank between “(“ and “see”

\textcolor{red}{JS: Seems to have been fixed by DLM.}

-Page 23, left column, caption of Figure 9 (first and last lines): k and T should be written in italic.

\textcolor{red}{JS: Fixed.}

-Page 24, right column, line 4 in second paragraph: There seems to be a non-fitting “the” in the sentence.

\textcolor{red}{JS: Fixed.}

-Page 24, right column, line 7 in third paragraph: Please remove blank between “]” and “.”

\textcolor{red}{JS: Fixed.}

-Page 25, left column, first line in second paragraph of section “Handling multiple …”: lignad -> ligand

\textcolor{red}{JS: Fixed.}

-Page 26, right column, figure 11: The “u” on the y-axis in the second panel might also be written in italics.

\textcolor{green}{JS: Should be fixed by the creator of the figure.}

-Page 27, right column, line 8 in second paragraph of section “Subsampling data to …”: “can be” appears twice.

\textcolor{red}{JS: Fixed.}

-Page 28, left column, line 21: should it be the “right hand side” instead of “left hand side”?

\textcolor{green}{JS: Should be fixed by JDC/JM/DLM.}

-Page 28, right column, Eq. (27): the $j$ in $f_ij$ should be subscript.

\textcolor{red}{JS: Fixed.}

-Page 28, right column, line 4 in paragraph 4: “that is asymptotically correct in …”. Is the “in” correct?

\textcolor{red}{JS: Fixed.}

-Page 28, right column, second last line from bottom: “than” should be “then”

\textcolor{red}{JS: Fixed.}

-Page 29, right column, line 4 from the bottom: is there a “that” missing in “… errors that are hard to estimate …”

\textcolor{red}{JS: Fixed.}

-Page 31, left column, line 2: is there a comma missing after “available”?

\textcolor{red}{JS: Fixed.}

-Page 33, left column, line 8 from bottom: “… minima are that are visited …” needs revision

\textcolor{red}{JS: Fixed.}

-Page 33, right column, line 4: The “or” does not fit here.

\textcolor{red}{JS: Fixed.}

-Page 34, left column, line 5 in second paragraph: “… have errors of show multiple …” needs revision.

\textcolor{red}{JS: Fixed.}

-Page 35, right column, line 6 from bottom: Please add blank between “module” and “[“.

\textcolor{red}{JS: Fixed.}

-Page 39, left column: line 3: Please add blank after “14,”

\textcolor{red}{JS: Fixed.}

-Page 40, ref [10]: Please abbreviate the journal name.

\textcolor{green}{JS: leaving refs up to Toni"}

-Page 45, ref [131]: Please abbreviate the journal name.

-Page 45, ref [155]: This paper has the title: “Incorporating the effect of ionic strength in free energy calculations using explicit ions”.

-Page 47, ref [189]: Please abbreviate the journal name.

-Page 48, ref [216]: Please provide a link here.

-Page 48, ref [224]: Please use abbreviations for the author names.

\textbf{Reviewer 3 Comments}

@@

For the amusement of the authors I should mention that while reading the following occurred to me four times in a row: at some point I thought: Hey, the following issue should be mentioned, took a note, did read on, and found precisely this issue discussed, and thus I deleted my note. I think that shows that the manuscript is really very well structured, always fulfilling the reader’s expectation what should come next!

(1) In Chap 3.1 Eq suggests that the law of mass action can be applied to calculate K_b and Delta G_B from MD simulations. I am aware the authors just mean to provide the conceptual background here, but I am similarly aware of a few groups that actually have used the LMA. This is very dangerous. As shown in [54], the LMA does not strictly hold for systems with very few particles, and it contradicts in fact the more fundamental and general eq (7). E.g., if a simulation system just contains one L and one R molecule, and these bind and unbind many times during the simulation, eq (7) would (correctly) predict that $\Delta G = -kT log Z(RL)/Z(R+L) \approx -kT log T(RL)/T(R+L)$, where the latter means the time fraction of the trajectory where the system is bound / unbound. In contrast, the LMA would (wrongly) claim that $\Delta G = -kT log [RL]/[R][L] \approx -kT log T(RL)/(T(R+L))^2$. The authors might want to add a word of caution to this not so well-known fact.

\textcolor{red}{AR: The referee raises a valid concern, and we have made the warning explicit in Section 3.2.}

@@

(10) Use larger fonts in Fig 2 &7, generally try to have equally-sized fonts throughout all Figs.

\textcolor{red}{JS: PR includes increased font sizes in figs 2 and 7. Additionally, slightly reformatted pane 7B to have a cleaner horizontal line}

\end{newlfm}

\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional Formal Letter
% LaTeX Template
% Version 1.0 (28/12/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Brian Moses (http://www.ms.uky.edu/~math/Resources/Templates/LaTeX/)
% with extensive modifications by Vel (vel@latextemplates.com)
%
% Further modifications including UoY specific changes by George Tsoulas 
% (george.tsoulas@gmail.com}
%
% A simple letter template with the University of York Logo mostly meant for % personal rather than departmental letters.
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%---------------------------------------------
% PACKAGES AND OTHER DOCUMENT CONFIGURATIONS |
%---------------------------------------------

\documentclass[11pt,a4paper]{letter} % Specify the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)

\usepackage{graphicx} % Required for including pictures
\usepackage{microtype} % Improves typography
\usepackage[T1]{fontenc} % Required for accented characters
\usepackage{fbb} %Use the free version of the Bembo font Family
\usepackage{xcolor}
\usepackage{hyperref}
%\usepackage{gfsdidot} % Use the GFS Didot font: http://www.tug.dk/FontCatalogue/gfsdidot/
%\usepackage{lipsum}
% Create a new command for the horizontal rule in the document which allows thickness specification
\makeatletter
\def\vhrulefill#1{\leavevmode\leaders\hrule\@height#1\hfill \kern\z@}
\makeatother

%-------------------
% DOCUMENT MARGINS |
%-------------------

\usepackage[left=1.2in,
top=1.25in,
right=1.25in,
bottom=1.25in,
headsep=0.25in,
headheight=20pt,
heightrounded]
{geometry}

%---------------------
% SENDER INFORMATION |
%---------------------

\def\Who{Antonia Mey} % Your name
\def\What{Dr } % Your title
\def\Where{School of Chemistry} % Your department/institution
\def\Address{University of Edinburgh} % Your address
\def\Address{David Brewster Road, EH9 3FJ} % Your address
\def\CityZip{} % Your city, zip code, country, etc
\def\Email{antonia.mey@ed.ac.uk} % Your email address
\def\URL{http://www.mey-research.org} % Your URL

%------------------------------------
% HEADER AND FROM ADDRESS STRUCTURE |
%------------------------------------

\address{\vspace*{-2.3cm}
  \includegraphics[width=1in]{Ylogo.png} %Include the logo of your institution
\hspace*{5in} % Position of the institution logo, increase to move left, decrease to move right
\hspace{-3in} \hfill \normalsize % Second line of institution name, adjust hspace if your logo is wide
\makebox[0ex][r]{\bf \What \Who }\hspace{0.08in} % Print your name and title with a little whitespace to the right
~\\[-0.03in] % Reduce the whitespace above the horizontal rule
\vspace*{-.08in}\hspace{.1in}\vhrulefill{1pt} \\ % Horizontal rule, adjust hspace if your logo is wide and \vhrulefill for the thickness of the rule
\hspace{\fill}\parbox[t]{2.85in}{ % Create a box for your details underneath the horizontal rule on the right
\footnotesize % Use a smaller font size for the details
% \Who \\ Your name if you want it again there
\em % all text after this will be italicized
\Where\\ % Your department
\Address\\ % Your address
%\CityZip\\ % Your city and zip code
\TEL\\ % Your phone number
\Email\\ % Your email address
\URL % Your URL
}
\hspace{-1.4in} % Horizontal position of this block, increase to move left, decrease to move right
\vspace{-1in} % Move the letter content up for a more compact look
}

%-----------------------
% TO ADDRESS STRUCTURE |
%-----------------------

\def\opening#1{\thispagestyle{empty}
{\centering\fromaddress \vspace{1.2in} \\ % Print the header and from address here, add whitespace to move date down
\hspace*{}\today\hspace*{\fill}\par} % Print today's date, remove \today to not display it
{\raggedright \toname \\ \toaddress \par} % Print the to name and address
\vspace{0.4in} % White space after the to address
\noindent #1 % Print the opening line
% Uncomment the 4 lines below to print a footnote with custom text
%\def\thefootnote{}
%\def\footnoterule{\hrule}
%\footnotetext{\hspace*{\fill}{\footnotesize\em Footnote text}}
%\def\thefootnote{\arabic{footnote}}
}

%----------------------
% SIGNATURE STRUCTURE |
%----------------------

\signature{\What \Who} % The signature is a combination of your name and title

\long\def\closing#1{
\vspace{0.1in} % Some whitespace after the letter content and before the signature
\noindent % Stop paragraph indentation
\hspace*{\longindentation} % Move the signature right
\parbox{\indentedwidth}{\raggedright
#1 % Print the signature text
\vskip 0.65in % Whitespace between the signature text and your name
\fromsig}} % Print your name and title

%--------------------------------------------------------------------------

\begin{document}

%-------------
% TO ADDRESS |
%-------------

\begin{letter}
{Living Journal of Computational Molecular Sciences\\
}
%% Add more lines as you wish

%
%-----------------
% LETTER CONTENT |
%-----------------

\opening{Dear Professor Oostenbrink,}

We would like to thank the reviewers for having taken the time to read the manuscript and to give such excellent feedback. Below we endeavor to address each of the comments in detail. All the suggestions and references from you, the editor, have also been included now, giving Gromos equally prominent space as other software packages in the manuscript.

\textbf{Reviewer 1 comments:}\\
(...)

@@

Figure 1: For me there is no intrinsic difference between the free energy calculations shown in panel D and F, both transformations should be performed in the bound and unbound states to obtain meaningful results, and both should be termed relative calculations ($\Delta \Delta$ G). Maybe it could be more clearly indicated in general if a whole molecule is decoupled and if only a part of a molecule is transformed?

\textcolor{red}{We used  $\Delta\Delta G$ instead of  $\Delta$ G; swapped E and F, made 'Host' and 'membrane' text larger and added interaction schematic (green) in D.}

@@

\textcolor{red}{We added a clarification to this in Sec. 4.1.}

Section 4.1, line 30: it is not entirely clear to me what the authors mean by "edges". This should be better explained in the text.

\textcolor{red}{We added a sentence in Sec. 4.1 to clarify this.}

@@

\textcolor{red}{We removed this link, as it didn't really add anything useful.}

@@

\textcolor{red}{Using $K_b$ consistently now.}

Section 5.4, last paragraph: I would call it "binding free energy prediction", not "binding energy prediction"

\textcolor{red}{Fixed.}

Constraints and relative free energy calculations: for me, a timestep of 1 fs is more an upper limit for MD simulations involving non-constrained bonds, I would rather suggest a value of 0.5 fs.

\textcolor{red}{ This is a valuable point to raise. Certainly 1.0 fs is near the limit of stability without any constraints with standard fields, and there are studies showing there are non-negligible statistical mechanical errors with timesteps of 1.0 fs. However, many studies with free energy calculations have been done with these parameters and it's not clear they have statistically significant deviation from simulations with smaller timesteps. We have added a discussion on timesteps to section 7.3 with a tentative recommendation that 1.0 fs may be acceptable.}

@@

\textcolor{red}{We changed the wording to clarify this point. The reweighting can be skipped if the ligand is never \textit{sampled} while hitting the wall because, in this case, the numerical correction is exactly zero. Using the restraint is different from using no restraining potential at all because during the MD simulation the ligand might still very occasionally hit the wall (thus limiting its volume to the binding site) even if we these events are not observed after subsampling the trajectory.}

@@

\textcolor{red}{We added the reference to the text.}

@@

\textcolor{red}{Both the text in the section and the figure were updated to include the forward/reverse convergence test.}

@@

\textcolor{red}{We have added Gromos to the software section and also added appropriate references to it throughout the manuscript.}

\textbf{Reviewer 2 Comments:}\\
Much of the discussion is related to alchemical free-energy calculations in drug design. I think that the success of such calculations is also very dependent on the force field. Although not a topic of the present manuscript, the authors may want to issue a recommendation/warning regarding the validation of automatically generated ligand topologies. I guess, many practitioners just take such topologies for granted.

\textcolor{red}{We have added explicit comments in section 4.1 with respect to the need for using reasonable parameter/topology input files that have been inspected to make sure the molecular description has no obvious errors, or lack of chemical coverage in the method used to generate them}

In the list of more advanced topics on page 3 the application to QM/MM simulations may be mentioned as well, since this seems to be an area of growing importance.

\textcolor{red}{We have added QM/MM and ML topics explicitly in that list and added some starting point references.}

At the end of section 7.1.1 on pages 15/16 the following statement appears: "Typical molecular dynamics engines are not set up to recognize this change, or at least not to correctly include contributions to the free energy from changing constraints/constraint length, so results for a transformation would usually be erroneous." This statement is a bit surprising since methods to calculate the contribution of the work done by constraint forces have been described a few times, e.g.: 
\begin{itemize}

    \item Van Gunsteren, W.F., In van Gunsteren W.F. and Weiner, P.K. (Eds.) Computer Simulation of Biomolecular Systems: Theoretical and Experimental Applications, ESCOM, Leiden, 1989, pp. 1-26.

    \item Pearlman, D.A., Kollman, P.A., The overlooked bond-stretching contribution in free energy perturbation calculations, J. Chem. Phys. 1991, 94(6), 4532-4545.

    \item Straatsma, T.P., Zacharias, M., McCammon, J.A., Holonomic constraint contribution to free energy differences from thermodynamic integration molecular dynamics simulations, Chem. Phys. Lett., 1992, 196(3-4), 297-302.

    \item Pearlman, D.A., Determining the contributions of constraints in free energy calculations: Development, characterization, and recommendations, J. Chem. Phys. 1993, 98(11), 8964-8957.

\end{itemize}
One implementation, based on integrating over the constraint forces, can for example be found in the MD code GROMOS. I suggest to mention the availability of both the theory and also practical implementations in the manuscript.

\textcolor{red}{We have revised this text in 7.1, making it clear that the corrections are known, that different programs vary in their implementation of the corrections, and that users should check the user manuals if they have bond lengths that both change and are constrainted. We also added the suggested references.}

In section 7.2.2, when discussing changes in net charge the "Double-system/single-box" setup described by Gapsys et al. may be mentioned. It is related to the alchemical ion approach but can be mentioned here for completeness and to help newcomers to the field in sorting the various approaches. Gapsys, V., Michielssens, S., Peters, J. H., DeGroot, B. L., Leonov, H. Calculation of Binding Free Energies, In Andreas Kukol (ed.), Molecular Modeling of Proteins, Methods in Molecular Biology, vol. 1215, doi: 10.1007/978-1-4939-1465-4\_9, Springer Science+Business Media New York 2015.

\textcolor{red}{We made appropriate corrections to this. }

@@

In the list of symbols on page 4, the quantity $\Delta G$ is denoted as Gibbs free energy while $\Delta A$ is denoted as Helmholtz free energy. However, according to IUPAC or IUPAP these quantities are referred to as Gibbs energy or Helmholtz energy (see \url{https://doi.org/10.1039/9781847557889} or \url{https://doi.org/10.1016/0378-4371(78)90209-1}) or sometimes also as "Gibbs function" or "Helmholtz function" or as "free enthalpy" or "free energy" respectively. Of course, the nomenclature used by authors is very common in the field. Therefore, one solution would be to use the IUPAC nomenclature in the List of Symbols along with a footnote explaining that here a different nomenclature is used (or the other way round).

\textcolor{red}{We have added the less-commonly used but also correct terms as alternate names for these quantities in the list of symbols.}

Eq. (2) holds for dilute solutions if thermodynamic activities can be approximated by concentrations. This is also stated in the classical Gilson paper but I guess repeating it here, could be useful.

\textcolor{red}{We now state this explicitly referencing the Gilson paper.}

Page 5: In statistical mechanics nomenclature the term "configuration" is usually used for $\vec{q}$. In chemistry and biology, the term "conformation" is probably more common. In the context of the present manuscript "configuration" fits better in my opinion.

\textcolor{red}{We updated this to use configuration consistently and explained that a conformation can be a set of configurations that can be grouped together into a metastable state.}

The quantity $\Delta G_{solvated}$ in Figure 2 is called $\Delta G_{unbound}$ in Eq. (9).

\textcolor{red}{We updated the labelling to make it consistent. }

In the first paragraph of section 4.2 it is mentioned that a good practice is to perform two or three runs of the same perturbation. Here one might add that the initial conditions (i.e. velocities) should be different.

\textcolor{red} {We have added this.}

Page 17, line 9 under Eq. (17): A, B, and AB may be replaced by R, L, and RL.

\textcolor{red} {We have fixed this.}

In the paragraph of author contributions, the description of the contribution of Samarjeet Prasad seems to be missing.

\textcolor{red} {The contributions were added.}

TYPOS OR OTHER EDITORIAL ISSUES
\begin{itemize}

   \item Page 3, right column, line 5 in third paragraph: preparation( Sec. 6) $\rightarrow$ preparation (Sec. 6)    
   \item Page 4, left column, list of acronyms: "unsigned error" should be written in upper case to be consistent with the other entries.

   \item Page 5, left column: In the nominator and denominator of Eqs (5) and (6) the minus sign is missing in the exponentials.

    \item Page 5, right column, first line: "one of the ..."

   \item Page 6, right column, two lines above Eq. 12: Bennet's $\rightarrow$ Bennett's

   \item Page 8, right column, fifth line below Eq. 16: enrgies  $\rightarrow$ energies
\end{itemize}
\textcolor{red}{All above have been fixed.}

Page 8, right column, 10th line below Eq 16: Perhaps the line break in the unit can be avoided.

\textcolor{red}{Fixed by changing line to ..If the accuracy of \textit{a collection of} free energy calculations is..}

Page 11, left column, paragraph 5.4: there are two occurrences of the term "binding energy prediction". Is "binding free energy prediction" meant?

\textcolor{red}{We have fixed these.}

Page 12, left column: "stereoisomers" is misspelled.

\textcolor{red}{This has been fixed.}

Page 15, Figure 4: the right structure in the lower part has no green area. Is that intended?

\textcolor{red}{We updated the caption to explain this further. }

Page 17, Eq. 18: the ratio of $c^o/V_L$ seems not correct. It should be either $V^o/V_L$ where $V^o$ is the volume corresponding to $c^o$, or, when sticking to $c^o$: $c^o * V_L$

\textcolor{red}{This has been fixed.}

Page 17, line 14: "restraints" (s was missing)

\textcolor{red}{This has been fixed.}

Page 19, Figure 7: The axis labels are hard to read.

\textcolor{red}{This has been fixed.}

Page 19, Eq. 19: I think it should be $(1-\lambda)U_0 + \lambda U_1$ to fit to the text below the equation

\textcolor{red}{Correct. This has been fixed.}

Page 20, left column, line 14: $\sigma/r$ should be written in parenthesis.

\textcolor{red}{This has been fixed.}

Page 20, left column, line 16: B in $k_{B}T$ should be in subscript and T not.

\textcolor{red}{This has been fixed.}

Page 20, left column, line 10 from the bottom: is there an "at" missing in "and at the other endpoint ..."?

\textcolor{red}{ Yes, this has been fixed.}

Page 22, left column, caption of Figure 8 (line 6): should there be a comma after "exchang"?

\textcolor{red}{this has been fixed.}

Page 22, right column, line 2: though $\rightarrow$ through

\textcolor{red}{This has been fixed.}

Page 22, right column, lines 8 and 9: Please add a blank between value and unit.

\textcolor{red}{This has been fixed.}

Page 22, right column, last line of second paragraph: Please remove blank between "(" and "see"

\textcolor{red}{This has been fixed.}

Page 23, left column, caption of Figure 9 (first and last lines): k and T should be written in italic.

\textcolor{red}{This has been fixed.}

Page 24, right column, line 4 in second paragraph: There seems to be a non-fitting "the" in the sentence.

\textcolor{red}{This has been fixed.}

Page 24, right column, line 7 in third paragraph: Please remove blank between "]" and "."

\textcolor{red}{This has been fixed.}

Page 25, left column, first line in second paragraph of section "Handling multiple ...": lignad  $\rightarrow$ ligand

\textcolor{red}{This has been fixed.}

Page 26, right column, figure 11: The "u" on the y-axis in the second panel might also be written in italics.

\textcolor{red}{This has been fixed.}

Page 27, right column, line 8 in second paragraph of section "Subsampling data to ...": "can be" appears twice.

\textcolor{red}{This has been fixed.}

Page 28, left column, line 21: should it be the "right hand side" instead of "left hand side"?

\textcolor{red}{This has been fixed.}

Page 28, right column, Eq. (27): the $j$ in $f_ij$ should be subscript.

\textcolor{red}{This has been fixed.}

Page 28, right column, line 4 in paragraph 4: "that is asymptotically correct in ...". Is the "in" correct?

\textcolor{red}{This has been fixed.}

Page 28, right column, second last line from bottom: "than" should be "then"

\textcolor{red}{This has been fixed.}

Page 29, right column, line 4 from the bottom: is there a "that" missing in "... errors that are hard to estimate ..."

\textcolor{red}{This has been fixed.}

Page 31, left column, line 2: is there a comma missing after "available"?

\textcolor{red}{This has been fixed.}

Page 33, left column, line 8 from bottom: "... minima are that are visited ..." needs revision

\textcolor{red}{This has been fixed.}

Page 33, right column, line 4: The "or" does not fit here.

\textcolor{red}{This has been fixed.}

Page 34, left column, line 5 in second paragraph: "... have errors of show multiple ..." needs revision.

\textcolor{red}{This has been fixed.}

Page 35, right column, line 6 from bottom: Please add blank between "module" and "[".

\textcolor{red}{This has been fixed.}

Page 39, left column: line 3: Please add blank after "14,"

\textcolor{red}{This has been fixed.}

Page 40, ref [10]: Please abbreviate the journal name.

\textcolor{red}{This has been fixed.}

Page 45, ref [131]: Please abbreviate the journal name.

\textcolor{red}{This has been fixed.}

Page 45, ref [155]: This paper has the title: "Incorporating the effect of ionic strength in free energy calculations using explicit ions".

\textcolor{red}{This has been fixed.}

Page 47, ref [189]: Please abbreviate the journal name.

\textcolor{red}{This has been fixed.}

Page 48, ref [216]: Please provide a link here.

\textcolor{red}{This has been fixed.}

Page 48, ref [224]: Please use abbreviations for the author names.

\textcolor{red}{This has been fixed.}

\textbf{Reviewer 3 Comments:}

@@

For the amusement of the authors I should mention that while reading the following occurred to me four times in a row: at some point I thought: Hey, the following issue should be mentioned, took a note, did read on, and found precisely this issue discussed, and thus I deleted my note. I think that shows that the manuscript is really very well structured, always fulfilling the reader's expectation what should come next!

(1) In Chap 3.1 Eq suggests that the law of mass action can be applied to calculate $K_b$ and Delta $G_B$ from MD simulations. I am aware the authors just mean to provide the conceptual background here, but I am similarly aware of a few groups that actually have used the LMA. This is very dangerous. As shown in [54], the LMA does not strictly hold for systems with very few particles, and it contradicts in fact the more fundamental and general eq (7). E.g., if a simulation system just contains one L and one R molecule, and these bind and unbind many times during the simulation, eq (7) would (correctly) predict that $\Delta G = -kT \log Z(RL)/Z(R+L) \approx -kT log T(RL)/T(R+L)$, where the latter means the time fraction of the trajectory where the system is bound / unbound. In contrast, the LMA would (wrongly) claim that $\Delta G = -kT log [RL]/[R][L] \approx -kT log T(RL)/(T(R+L))^2$. The authors might want to add a word of caution to this not so well-known fact.

\textcolor{red}{The referee raises a valid concern, and we have made the warning explicit in Section 3.2.}

@@

\textcolor{red}{We added a couple of sentences to highlight this in section 7.2.5 and 8.4}

(10) Use larger fonts in Fig 2 and 7, generally try to have equally-sized fonts throughout all Figs.

\textcolor{red}{We increased the font sizes in figs 2 and 7. Additionally, slightly reformatted pane 7B to have a cleaner horizontal line}
